\newpage
\section{Conclusions}
\label{S6}
/{Present your conclusions and recommendations.}/\cite{sharpe}\cite{gnuplot}

The choice of implementing either of the two designs is influenced by more factors than the results of a reliability evaluation as conducted in this laboratory assignment. Other properties that is of value is for example cost, maintainability, and modifiability. The cost is of coarse of major concern and the maintenance can be a significant part of the life-time cost. It is hard for us to guess about any cost differences, as the two systems utilize the same amount of hardware. One point in favor for the centralized architecture is that it is probably easier to physically replace a computer module in the CU than in a WU. 

A vehicle manufacture probably gathers all CUs from several systems in one physical place and probably also let several system to run on the same computer modules. If all systems in the vehicle follow the same principles, to focus the computing power to the CUs and to place all the CUs together, maintenance is simplified. When using such a approach, the centralized design is easier integrated with the rest of the system. Modifiability will also be favored if a centralized design is used together with multiple systems sharing the same computer modules, because then can processing power be moved between the systems as new versions of software is released which has different processing demands. %However, as we know that a system with a lot of hardware and a high software complexity increases the failure rate of the entire system, it is not an easy task to integrate several systems tightly. <- kn as i gt

The assumptions used in this evaluation will not hold in a real system, but to get a broad picture of the design benefits without using to complicated models, the assumptions are favorable. Likewise, the life-time of a vehicle is longer than the evaluated period of four years, but the reliability tendencies can easily be spotted in the results obtained from the evaluated period.


conclusion:

